---
title: "Plots using plotly"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---


We will be looking at the NYC Restaurant violations data

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(lubridate)

```

## Using NYC restaurants inspection data 

```{r}
data("rest_inspec")

rest_inpec_clean = 
  rest_inspec %>% 
  janitor::clean_names() %>%
  mutate(zipcode = as.factor(zipcode)) %>%
drop_na(score) %>%
drop_na(boro)
```
Wrangling data for to remove duplicate scores for the same restaurant for the same inspection date:

```{r}
rest_no_dup = rest_inpec_clean %>%
  select(dba,boro,zipcode, inspection_date, score, grade)

rest_no_dup = rest_no_dup %>% 
  distinct(dba,boro, zipcode, inspection_date, score, grade)
```

### First plot: Making a scatterplot of inspection dates versus zipcodes showing when the restaurants were inspected and what grade they received

```{r}
rest_no_dup %>%
  filter(boro == "MANHATTAN") %>%
  drop_na(grade) %>%
  mutate(text_label = str_c("Restaurant name: ", dba, " Grade: ", grade)) %>% 
  plot_ly(
    x = ~zipcode, y = ~inspection_date, type = "scatter", mode = "markers",
    color = ~grade, text = ~text_label, alpha = 0.7)
```


### Second plot: Box plot for scores by zip code in Manhattan

```{r}
rest_no_dup %>%
  filter (boro =="MANHATTAN")%>%
  plot_ly(y = ~score, x = ~zipcode, color = ~zipcode, type = "box", colors = "viridis")
```

### Third plot: Top 20 Restaurants in Manhattan with the highest number of violations

```{r}
rest_inpec_clean %>%
  filter(boro=="MANHATTAN") %>%
  group_by(dba) %>%
  summarise(n=n())%>%
  top_n(20)%>%
  plot_ly(x = ~dba, y = ~n, color = ~dba, type = "bar", colors = "viridis")
```
